\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-29 Paper/Paper.tex
add Grad-CAM's autocite.

	We can use Grad-CAM to highlight areas on the image that make a large contribution to the final classification \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra}. If the model had been trained correctly, this would be equivalent to highlighting the abnormity. Fig.~\ref{fig:gradCAM} shows some examples. Furthermore, Grad-CAM can highlight a designated abnormity, so it may be able to highlight multiple abnormities on one image, as shown in Fig.~\ref{fig:gradCAM_multi_abnormity}.

>>>>

	We can use Grad-CAM \autocite{Selvaraju_Cogswell_Das_Vedantam_Parikh_Batra} to highlight areas on the image that make a large contribution to the final classification. If the model had been trained correctly, this would be equivalent to highlighting the abnormity. Fig.~\ref{fig:gradCAM} shows some examples. Furthermore, Grad-CAM can highlight a designated abnormity, so it may be able to highlight multiple abnormities on one image, as shown in Fig.~\ref{fig:gradCAM_multi_abnormity}.
